### 2023-12-20 manuscript.tex
add abbreviations [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/3587e45ed5b57a2b3dda176e1e9881404c079911.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/3587e45ed5b57a2b3dda176e1e9881404c079911/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/7273348131

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/84a03aa1376ce7a4793ae4c2260615baa8ed7714/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/84a03aa1376ce7a4793ae4c2260615baa8ed7714}{MMV-Lab/im2im-paper@84a03aa}
on December 18, 2023.

@@

\emph{3D Labelfree:} We tested with 3D images from the hiPS single cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}. Specifically, we extracted the brightfield channel and the structure channel from the full field-of-view (FOV) multi-channel images, from the HIST1H2BJ, FBL, NPM1, LMNB1 cell lines, so as to predict from one brightfield image various nuclear structures, histones, nucleoli (dense fibrillar component via fibrillarin), nucleoli (granular component via nucleophosmin), and nuclear envelope, respectively. Images were acquired at 100x with 1.25 NA (voxel size: 0.108 micron x 0.108 micron x 0.29 micron).

@@

In this work, we tested on both 2D and 3D instance segmentation problems. Going from 2D to 3D is not a simple generalization from 2D models by switching 2D operations with 3D operations, but with many practical challenges. Large GPU footprint is one of the biggest issues, which makes many training strategies common in 2D not feasible in 3D, e.g.~limited mini-batch size. \emph{MMV\_Im2Im} is able to take advantage of state-of-the-art ML engineering methods to efficiently handle 3D problems. For example, by using effective half-precision training, one can greatly reduce GPU memory workload for each sample and therefore increase the batch size or the patch size. When multiple GPUs are available, it is also possible to easily take advantage of the additional resources to scale up the training to multiple GPU cards, even multiple GPU nodes. As a demonstration, we applied \emph{EmbedSeg}-like models to a 2D problem of segmenting \emph{C. elegans} from widefield images {[}\protect\hyperlink{ref-138foKNOh}{41}{]}, as well as a 3D problem of nuclear segmentation from fluorescent and brightfield images from the hiPS single cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}.

@@

To perform unsupervised learning, we used raw images from the hiPS single-cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}, as well as their corresponding segmentations (may not be absolute pixel-wise ground truth, but have gone through systematic evaluation to ensure the overall quality). We shuffled the raw images and their segmentations to generate a set of simulated segmentation masks. A demonstration of the concept is illustrated in Figure \ref{fig:unsupervised}-A. Example results for all 3D models are shown in Figure \ref{fig:unsupervised}-B, and the F1-scores on the test set are summarized in Table \ref{tbl:unsuper}.

@@

Generating a large amount of synthetic microscopy images can be an important step in developing image analysis methods. Synthetic images offer a way to train other DL models, such as self-supervised pre-training, using a diverse set of images without the need for large amounts of real-world data. As long as the synthetic images are generated with sufficient quality, it is possible to have an unlimited amount of training data for certain applications. Moreover, synthetic images can be used to evaluate other models when validation data is difficult to obtain. In this study, we demonstrate that \emph{MMV\_Im2Im} can generate 2D/3D synthetic microscopy images with high realism and validity, using a subset of data collected from the hiPS single-cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}, either in a supervised or unsupervised manner.

@@

This dataset weas downloaded from {[}?? stain\_tranformation{]}, which was released with the publication {[}\protect\hyperlink{ref-WwenuBHa}{5}{]}. We used the dataset ``BC-DeepLIIF\_Training\_Set.zip'' and ``BC-DeepLIIF\_Validation\_Set.zip''. In our three experiments, we always used the IHC image as the input, and used standard hematoxylin stain image, mpIF nuclear image and mpIF LAP2beta image as ground truth, correspondingly.

@@

\begin{itemize}
\tightlist
\item
  Deep Learning (DL)
\end{itemize}

@@

@@

@@

We would like to thank the MONAI team for their support in our process of development, and the aicsimageio team for advice on how to integrate aicsimageio into the package. This work is supported by the Federal Ministry of Education and Research (Bundesministerium für Bildung und Forschung, BMBF) under the funding reference 161L0272, and by the Ministry of Culture and Science of the State of North Rhine-Westphalia (Ministerium für Kultur und Wissenschaft des Landes Nordrhein-Westfalen, MKW NRW).

@@

\leavevmode\vadjust pre{\hypertarget{ref-b6GmFJlO}{}}%
\CSLLeftMargin{55. }%
\CSLRightInline{\textbf{Content Aware Image Restoration: Pushing the Limits of Fluorescence Microscopy - Supplemental Data}
\CSLBlock{Martin Weigert, Uwe Schmidt} \url{https://publications.mpi-cbg.de/publications-sites/7207/}}

@@

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/3587e45ed5b57a2b3dda176e1e9881404c079911/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/3587e45ed5b57a2b3dda176e1e9881404c079911}{MMV-Lab/im2im-paper@3587e45}
on December 20, 2023.

@@

\emph{3D Labelfree:} We tested with 3D images from the hiPSC single cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}. Specifically, we extracted the brightfield channel and the structure channel from the full field-of-view (FOV) multi-channel images, from the HIST1H2BJ, FBL, NPM1, LMNB1 cell lines, so as to predict from one brightfield image various nuclear structures, histones, nucleoli (dense fibrillar component via fibrillarin), nucleoli (granular component via nucleophosmin), and nuclear envelope, respectively. Images were acquired at 100x with 1.25 NA (voxel size: 0.108 micron x 0.108 micron x 0.29 micron).

@@

In this work, we tested on both 2D and 3D instance segmentation problems. Going from 2D to 3D is not a simple generalization from 2D models by switching 2D operations with 3D operations, but with many practical challenges. Large GPU footprint is one of the biggest issues, which makes many training strategies common in 2D not feasible in 3D, e.g.~limited mini-batch size. \emph{MMV\_Im2Im} is able to take advantage of state-of-the-art ML engineering methods to efficiently handle 3D problems. For example, by using effective half-precision training, one can greatly reduce GPU memory workload for each sample and therefore increase the batch size or the patch size. When multiple GPUs are available, it is also possible to easily take advantage of the additional resources to scale up the training to multiple GPU cards, even multiple GPU nodes. As a demonstration, we applied \emph{EmbedSeg}-like models to a 2D problem of segmenting \emph{C. elegans} from widefield images {[}\protect\hyperlink{ref-138foKNOh}{41}{]}, as well as a 3D problem of nuclear segmentation from fluorescent and brightfield images from the hiPSC single cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}.

@@

To perform unsupervised learning, we used raw images from the hiPSC single-cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}, as well as their corresponding segmentations (may not be absolute pixel-wise ground truth, but have gone through systematic evaluation to ensure the overall quality). We shuffled the raw images and their segmentations to generate a set of simulated segmentation masks. A demonstration of the concept is illustrated in Figure \ref{fig:unsupervised}-A. Example results for all 3D models are shown in Figure \ref{fig:unsupervised}-B, and the F1-scores on the test set are summarized in Table \ref{tbl:unsuper}.

@@

Generating a large amount of synthetic microscopy images can be an important step in developing image analysis methods. Synthetic images offer a way to train other DL models, such as self-supervised pre-training, using a diverse set of images without the need for large amounts of real-world data. As long as the synthetic images are generated with sufficient quality, it is possible to have an unlimited amount of training data for certain applications. Moreover, synthetic images can be used to evaluate other models when validation data is difficult to obtain. In this study, we demonstrate that \emph{MMV\_Im2Im} can generate 2D/3D synthetic microscopy images with high realism and validity, using a subset of data collected from the hiPSC single-cell image dataset {[}\protect\hyperlink{ref-5sGcmDuy}{26}{]}, either in a supervised or unsupervised manner.

@@

This dataset was downloaded from {[}\protect\hyperlink{ref-cjAzGPun}{57}{]}, which was released with the publication {[}\protect\hyperlink{ref-WwenuBHa}{5}{]}. We used the dataset ``BC-DeepLIIF\_Training\_Set.zip'' and ``BC-DeepLIIF\_Validation\_Set.zip''. In our three experiments, we always used the IHC image as the input, and used standard hematoxylin stain image, mpIF nuclear image and mpIF LAP2beta image as ground truth, correspondingly.

@@

\begin{itemize}
\tightlist
\item
  Artificial intelligence (AI)
\item
  Convolutional recurrent neural network (CRNN)
\item
  Deep learning (DL)
\item
  Fully convolutional network (FCN)
\item
  Graphics processing unit (GPU)
\item
  Human induced pluripotent stem cells (hiPSC)
\item
  Machine learning (ML)
\item
  Multiplex immunofluorescence (mpIF)
\item
  Research and development (R\&D)
\item
  Stimulated emission depletion (STED)
\end{itemize}

@@

This work is supported by the Federal Ministry of Education and Research (Bundesministerium für Bildung und Forschung, BMBF) under the funding reference 161L0272, and by the Ministry of Culture and Science of the State of North Rhine-Westphalia (Ministerium für Kultur und Wissenschaft des Landes Nordrhein-Westfalen, MKW NRW).

@@

J.C. planned the project and implemented most of the software. J.S. tested the software and ran all the experiments. Y.Z. added Docker support to the software, while J.S. and Y.Z. contributed minor fixes to the code. J.C. wrote the paper together with J.S., Y.Z. contributed to proofreading.

@@

We would like to thank the MONAI team for their support in our process of development, and the aicsimageio team for advice on how to integrate aicsimageio into the package.

@@

\leavevmode\vadjust pre{\hypertarget{ref-b6GmFJlO}{}}%
\CSLLeftMargin{55. }%
\CSLRightInline{\textbf{Content Aware Image Restoration: Pushing the Limits of Fluorescence Microscopy - Supplemental Data}
\CSLBlock{Martin Weigert, Uwe Schmidt, Tobias Boothe, Andreas Müller, Alexandr Dibrov, Akanksha Jain, Benjamin Wilhelm, Deborah Schmidt, Coleman Broaddus, Sian Culley, Eugene W Myers} \url{https://publications.mpi-cbg.de/publications-sites/7207/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-cjAzGPun}{}}%
\CSLLeftMargin{57. }%
\CSLRightInline{\textbf{Deep Learning-Inferred Multiplex ImmunoFluorescence for Immunohistochemical Image Quantification}
\CSLBlock{Parmida Ghahremani, Yanyun Li, Arie Kaufman, Vanguri Rami, Noah Greenwald, Michael Angelo, Travis Hollmann, Saad Nadeem} \emph{Zenodo} \url{https://zenodo.org/record/4751737\#.Y9gbv4HMLVZ}}
